%%%%%%%%%%%%%%%%%%%%%%%% referenc.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% sample references
% "computer science"
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%

%
% BibTeX users please use
% \bibliographystyle{}
% \bibliography{}
%
% Non-BibTeX users please use
\begin{thebibliography}{99.}
%
% and use \bibitem to create references.
%
% Use the following syntax and markup for your references
%
% Contributed Works
\bibitem{contribution1} Edmundson, A., Holtkamp, B., Rivera, E., Finifter, M., Mettler, A., Wagner, D. (2013). 
An empirical study on the effectiveness of security code review. In Engineering Secure Software and Systems 
(pp. 197-212). Springer Berlin Heidelberg.

\bibitem{contribution9} Bacchelli Alberto, and Christian Bird. 
"Expectations, outcomes, and challenges of modern code review." 
Proceedings of the 2013 International Conference on Software Engineering. IEEE Press, 2013.

\bibitem{contribution20} Czerwonka Jacek, Michaela Greiler and Jack Tilford. Code Reviews Do Not Find Bugs. 
How the Current Code Review Best Practice Slows Us Down. 
Proceedings of the 2015 International Conference on Software Engineering. IEEE Publisher, 2015.

\bibitem{contribution10} Tao Zhang; Byungjeong Lee "A Bug Rule Based Technique with Feedback for Classifying Bug Reports",  
Computer and Information Technology (CIT), 2011 IEEE 11th International Conference on, On page(s): 336 - 343 

\bibitem{contribution11} IaaS cloud computing of Rackspace Cloud and NASA: https://it.wikipedia.org/wiki/OpenStack and 
https://www.openstack.org

\bibitem{contribution12} Bug Tracking for OpenStack. https://it.wikipedia.org/wiki/Launchpad

\bibitem{contribution13} Gerrit Code Review for OpenStack. //review.openstack.org/Documentation/intro-quick.html

\bibitem{contribution14} D. L. Parnas and M. Lawford. Inspection's role in software quality assurance. In 
Software, IEEE,  vol. 20, 2003. 

\bibitem{contribution15} M. E. Fagan. Design and Code inspections to reduce errors in program development. In IBM Systems Journal 15 
pp. 182-211, 1976. 

\bibitem{contribution17} P. M. Johnson, and D. Tjahjono. Does Every Inspection Really Need a Meeting? In Empirical Software Engineering, vol. 3, 
no. 1, pp. 9-35, 1998. 

\bibitem{contribution18} P. McCarthy, A. Porter, H. Siy et al. An experiment to assess cost-benefits of inspection meetings and their 
alternatives: a pilot study. In Proceedings of the 3rd International Symposium on Software Metrics: From Measurement to Empirical 
Results, 1996. 

\bibitem{contribution19} A. Porter, H. Siy, C. A. Toman et al. An experiment to assess the cost-benefits of code inspections in 
large scale software development. In SIGSOFT Softw. Eng. Notes, vol. 20, no. 4, pp. 92-103, 1995. 

\bibitem{contribution16} D. E. Perry, A. Porter, M. W. Wade. Reducing inspection interval in large-scale software development. In Software 
Engineering, I EEE Transactions on, vol. 28, no. 7, pp. 695-705, 2002. 

\bibitem{contribution2} Broy M (2002) Ayewah, N., Hovemeyer, D., Morgenthaler, J. D., Penix, J., Pugh, W. (2008). 
Using static analysis to find bugs. Software, IEEE, 25(5), 22-29.

\bibitem{contribution3} W. R. Bush, J. D. Pincus, D. J. Sielaff. “A static
analyzer for finding dynamic programming errors,” Softw.
Pract. Exper.
, vol. 30, no. 7, pp. 775–802, 2000.

\bibitem{contribution4} Hallem, D. Park, and D. Engler, “Uprooting software
defects at the source,”
Queue, vol. 1, no. 8, pp. 64–71, 2003.

\bibitem{contribution5} B. Chess and J. West,
Secure Programming with Static
Analysis, 1st ed.  Addison-Wesley Professional, Jul. 2007.

\bibitem{contribution6} N. Kennedy.  How google does web-based code reviews with mondrian.
http://www.test.org/doe/, Dec. 2006.

\bibitem{contribution7} A.  Tsotsis.  Meet  phabricator,  the  witty  code  review  tool  built  inside
facebook.  http://techcrunch.com/2011/08/07/oh-what-noble-scribe-hath-
penned-these-words/, Aug. 2006.

\bibitem{contribution8} Gerrit code review - https://www.gerritcodereview.com/ 

\bibitem{contribution21} J.  M.  Gonzalez-Barahona,  G.  Robles,  and  D.  Izquierdo-Cortazar.   The
metricsgrimoire  database  collection.   In
12th  Working  Conference  on
Mining Software Repositories (MSR)
, pages 478–481, May 2015

\bibitem{contribution22} http://activity.openstack.org/dash/browser/data/db/


\end{thebibliography}
